### 2015-05-08 fundamentals/intro.tex
restoring sentence with pairs.
Reviewer 2: page 3 (Background): With few exceptions, these metrics are derived from mass balances calculated by a fuel cycle simulator. [4]. : It would be nice to illustrate what are the few exceptions. Please read C. Poinssot, S. Bourg, N. Ouvrier, N. Combernoux, C. Rostaing, M. Vargas-Gonzalez et J. Bruno, Assessment of the environmental footprint of nuclear energy systems. Comparison between closed and open fuel cycles., Energy, n1In Press, pp. 1-13, 2014

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from 
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid,
fleet-based, or privately distributed. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental sustainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

>>>>

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid rather than
flexible, fleet-based rather than discrete, or privately distributed rather
than open source. Each of these choices presents a challenge to modeling
fidelity, generality, efficiency, robustness, and scientific transparency.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental sustainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions (e.g. 
\cite{poinssot_assessment_2014}, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.
